Dynein walks like an Imperial AT-ST

### 2018-08-16 papers/paper/paper.tex
Minor change to model fig caption

\begin{figure}[tbhp]
\includegraphics[width=0.4\linewidth]{../../plots/burgess-model-figure.pdf}%
\includegraphics[width=0.6\linewidth]{../../plots/grotjahn-model-figure.pdf}%
%% \includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Green bg:} Model superimposed over an axonemal dynein c micrograph consisting of an apo and and ADP-Pi-bound dynein monomer \cite{burgess-paper}; axonemal and cytoplasmic dynein have comparable size and architecture \cite{dynein-c-paper}. \textit{Grey bg:} Model superimposed over full-length dimerized dynein bound to accessory proteins \cite{grotjahn}. }
\label{fig:duration-length}
\end{figure}

%% \textit{Black bg:} Model superimposed over crystal structures of two monomers, pink being the ADP-Pi-bound cytoplasmic dynein-2 monomer from human (PDB ID 4RH7), yellow being an apo cytoplasmic dynein monomer from yeast (PDB ID 3VKH), docked together using linkers as a reference point. Orange indicates the linker region used to dock the two monomers. Left figure has a scale bar of 15nm, middle 26.3nm and right 28.8nm between the two binding domains.

@@

\begin{figure}[tbhp]
  \centering
   \includegraphics[width=0.3\columnwidth]{figures/schematic-1-cryoem}
   \includegraphics[width=0.3\columnwidth]{figures/schematic-1-superimposed}
   \includegraphics[width=0.3\columnwidth]{figures/schematic-1-model}

   \includegraphics[width=0.3\columnwidth]{figures/schematic-2-cryoem}
   \includegraphics[width=0.3\columnwidth]{figures/schematic-2-superimposed}
   \includegraphics[width=0.3\columnwidth]{figures/schematic-2-model}
   \caption{\textbf{Model schematic superimposed on cryo-EM images of
       native dynein.} Native cryo-EM images of the full dimerized
     dynein complex composed of light, intermediate and heavy chains,
     from \cite{nativestructure}. Model schematics are superimposed
     for illustrative purpose; shown angles to not represent expected
     \textit{in vivo} equilibria. Schematics are shown docked to a
     microtubule for illustrative purposes.}
   \label{fig:modelparams}
\end{figure}

\begin{figure}[tbhp]
  \centering
\includegraphics[width=0.5\columnwidth]{figures/schematic-prestroke}%
\includegraphics[width=0.5\columnwidth]{figures/schematic-poststroke}\\
\includegraphics[width=0.5\columnwidth]{figures/schematic-binding-angle}%
\includegraphics[width=0.5\columnwidth]{figures/schematic-full}
  \caption{\textbf{Schematic of model equilibrium angles over cryo-EM
      images.} \textbf{a.)} Prestroke and \textbf{b.)} poststroke
    dynein heavy chains superimposed with model motor angles, both
    from \cite{burgess-paper}. \textbf{c.)} Axonemal dynein bound to
    MT with model binding angle superimposed, from
    \cite{leschziner}. \textbf{d.} Full native dynein cryo-EM image
    bound to an MT with model superimposed, from
    \textbf{nativestructure}.}
\label{fig:modelangles}
\end{figure}

>>>>

\begin{figure}[tbhp]
\includegraphics[width=0.4\linewidth]{../../plots/burgess-model-figure.pdf}%
\includegraphics[width=0.6\linewidth]{../../plots/grotjahn-model-figure.pdf}%
%% \includegraphics[width=0.3\linewidth]{../../plots/crystal-model-figure.pdf}%
\caption{\textbf{Hinge model compared with dynein micrographs.} \textit{Left:} Model superimposed over an axonemal dynein c micrograph consisting of an apo and and ADP-Pi-bound dynein monomer \cite{burgess-paper}; axonemal and cytoplasmic dynein have comparable size and architecture \cite{dynein-c-paper}. \textit{Right:} Model superimposed over full-length dimerized dynein bound to accessory proteins, (map ID EMD-7000) \cite{grotjahn}. Left figure has a scale bar of 15nm, right 26.3nm between MTBD and AAA1 of motor domain.}
\label{fig:duration-length}
\end{figure}

%% \textit{Black bg:} Model superimposed over crystal structures of two monomers, pink being the ADP-Pi-bound cytoplasmic dynein-2 monomer from human (PDB ID 4RH7), yellow being an apo cytoplasmic dynein monomer from yeast (PDB ID 3VKH), docked together using linkers as a reference point. Orange indicates the linker region used to dock the two monomers.

@@

%% \begin{figure}[tbhp]
%%   \centering
%%    \includegraphics[width=0.3\columnwidth]{figures/schematic-1-cryoem}
%%    \includegraphics[width=0.3\columnwidth]{figures/schematic-1-superimposed}
%%    \includegraphics[width=0.3\columnwidth]{figures/schematic-1-model}

%%    \includegraphics[width=0.3\columnwidth]{figures/schematic-2-cryoem}
%%    \includegraphics[width=0.3\columnwidth]{figures/schematic-2-superimposed}
%%    \includegraphics[width=0.3\columnwidth]{figures/schematic-2-model}
%%    \caption{\textbf{Model schematic superimposed on cryo-EM images of
%%        native dynein.} Native cryo-EM images of the full dimerized
%%      dynein complex composed of light, intermediate and heavy chains,
%%      from \cite{nativestructure}. Model schematics are superimposed
%%      for illustrative purpose; shown angles to not represent expected
%%      \textit{in vivo} equilibria. Schematics are shown docked to a
%%      microtubule for illustrative purposes.}
%%    \label{fig:modelparams}
%% \end{figure}

%% \begin{figure}[tbhp]
%%   \centering
%% \includegraphics[width=0.5\columnwidth]{figures/schematic-prestroke}%
%% \includegraphics[width=0.5\columnwidth]{figures/schematic-poststroke}\\
%% \includegraphics[width=0.5\columnwidth]{figures/schematic-binding-angle}%
%% \includegraphics[width=0.5\columnwidth]{figures/schematic-full}
%%   \caption{\textbf{Schematic of model equilibrium angles over cryo-EM
%%       images.} \textbf{a.)} Prestroke and \textbf{b.)} poststroke
%%     dynein heavy chains superimposed with model motor angles, both
%%     from \cite{burgess-paper}. \textbf{c.)} Axonemal dynein bound to
%%     MT with model binding angle superimposed, from
%%     \cite{leschziner}. \textbf{d.} Full native dynein cryo-EM image
%%     bound to an MT with model superimposed, from
%%     \textbf{nativestructure}.}
%% \label{fig:modelangles}
%% \end{figure}
